NFC and burnout in teachers - A replication and extension study

### 2022-07-21 Manuscript/Revision_Letter.Rmd
answered abstract comment

> While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.

@@

\Assignment{JZ}
\WorkInProgress
\Easy

@@

We like to thank the reviewer very much for this positive assessment of our manuscript. In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p. XX.

@@

[address frist sentence] We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.

>>>>

> Burnout has become more prevalent, mainly in social jobs, and there is evidence that certain personality traits promote or protect against burnout. Only recently, studies have focused on investment traits like Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.

@@

Thank you for this suggestion.
We have changed the numbering of the supplementary material into a S2.1, S2.2, ... notation.

@@

We like to thank the reviewer very much for this positive assessment of our manuscript.
In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p. XX.
In our initial submission, there was an error in the code creating the table, so the diagonal with Cronbach's $\alpha$ and MacDonald's $\omega$ was missing.

@@

Thank you for pointing this out.
We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.
In fact, the limit of 150 words is so small that we cannot include all variable names, so we rewrote the abstract to better explain the three aims of the study.
It now reads as follows:

> Burnout has become more prevalent, mainly in social jobs, and there is evidence that certain personality traits promote or protect against burnout. Only recently, studies have focused on investment traits like Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities. This study had three aims: First, replicating findings of NFC and the burnout subscale reduced personal efficacy in student teachers in a sample of N = 180 teachers, second, investigating the role of perceived ratios of demands and resources in the context of NFC and burnout, and finally, creating an exploratory model as a starting point for future research. The results indicated that unlike the student sample, the teachers’ association of NFC and reduced personal efficacy was mediated by self-control but not reappraisal. Teachers with higher NFC and self-control also had lower burnout because they experienced their resources as fitting to the demands.
